---
title: "BCM"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BCM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# About
This package contains information about various courses offered by BCM college along with student performance over the year.

B.C.M. College Kottayam - Bishop Chulaparambil Memorial College

* **Website**: https://bcmcollege.ac.in
* **Phone**: +91 4812562171
* **Email**: bcmktm@yahoo.com

The college motto is SAPIENTIA ET GRATIA i.e. WISDOM AND GRACE, the two essential qualities in a woman. Believing that the true purpose of education is the  overall development of personality, the college tries to promote spiritual and moral growth along with intellectual development. It is expected that when a student leaves the portals of B.C.M. after her education, she will have become what our founder visualized as the ideal educated woman, one who combines in her wisdom and grace.

B.C.M College aims at the integral personalized education of the young. It strives to mold intellectually well trained, morally upright, socially committed, spiritually inspired men and women for the India of today.

```{r setup}
packageDescription("BCM")
news(package = "BCM")

library(BCM)
getNamespaceExports("BCM")

?bcm_programs
?bcm_papers
?bcm_results
?bcmdata

bcm_programs()
bcm_papers()
bcm_results()
```
